Risk Perceptions for Wearable Devices

### 2015-01-08 wearables_survey.tex
lots of wordsmithing

\section{Introduction}
With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing. Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking. Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and one of the top 25 market research companies estimates that 52\% of technology consumers are aware of wearables and among those, 33\% said they were likely to buy one~\cite{NPD}.

@@

To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}. A better understanding of users' risk perceptions will enable researchers and companies to focus on users' greatest concerns. The goal of this paper is to gain a better sense of what those concerns might be.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We compare users' perceptions of a wide range of privacy and security risks with wearable devices. Users care much more about the recipient of the data, than the type of data.
\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
\item Our participants viewed the data-collection capabilities of wearable devices as benign compared to more accepted technologies. However, we suspect that this may be due to their lack of exposure to these newer technologies.
%\item We report people's self-reported top concerns for wearable devices. Privacy, by far, is the top concern. Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms. 
\end{itemize}

@@

\subsection{Methodology Motivation}
\subsubsection{Smartphone Risk Scenarios}
Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risk scenarios. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
Our methodology follows that study closely, but with a different set of scenarios chosen to shed light on security and privacy risks of wearable devices.

\subsubsection{Technology Risk Perception}
Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}. In their study, participants were asked to separately rate the risks and benefits of these technologies. They were told to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10).
We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.

@@

We randomized the order in which participants completed each section of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of the questions within each section.

@@

We created an initial pool of 304 questions by combining 88 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios in order to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented each participant with 2 of the following 5 questions: \\[-.8cm]

@@

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies and how those perceptions compared to other well-established technologies. To this end, we modeled this section of the survey after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to rank several technologies by their relative risk and benefit to society. We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity. We chose these technologies because they represented varying levels of risks and benefits.

@@

\subsubsection{Additional Questions}
The exit portion of the survey consisted of standard demographics questions such as age, gender, and education. We also asked participants if they owned a wearable device so that we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices. Finally, we included the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so that we could control for participants' general privacy attitudes.

@@

\subsection{Recruitment and Analysis Method}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18 years old, living in the United States, and having a successful HIT completion rate of 95\% or above. Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants. We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784. Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).

@@

\subsection{Concern Factors}
In this section, we discuss the factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable device or a smartphone. We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of these factors, including demographic traits.

\subsubsection{Data Type}
Based on our data, we observed that the largest effect stemmed from the type of data being shared in a given scenario. We present various statistical models in section \ref{sec:regression} to support this conclusion. Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types. The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.

@@

Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior. For instance, demographic information (e.g., age, gender, language spoken). It is possible that people rated some of these as unconcerning because they believed that many entities already track this data (e.g., shows watched, music listened to, exercise patterns).

@@

\subsubsection{Data Recipient}
Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher. A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}). However, these effect sizes were relatively small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

We note that this chi-square test violates the assumption of independence of observations, since each participant responded to multiple scenarios. However, based on the randomization of treatments and very large sample size, we do not believe that this impacted our results. Nonetheless, we repeated the analysis using only one randomly-selected data point per participant and found that the test was robust to this violation: participants were significantly more concerned about having their data seen by actual humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups were not significant (i.e., between the public, friends, and work contacts).

@@

We compared the 10 most concerning scenarios when sharing with an app's servers versus with a human audience (friends, work contacts, and the public). We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]

@@

\subsubsection{Device Type}
Participants had unique VUR rates for situations only differing in the device. Our participants had a 58.79\% VUR when asked about wearables devices and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}. However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.  The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. There were too few instances where a participant got both versions of questions (34 in total for all 5 questions), to be able to perform a within-subjects analysis.

@@

We observed that participants' responses to our scenarios were correlated with several demographic factors. First, we observed that by far the biggest factor in participants' decisions to rate a scenario as very upsetting was their self-reported general privacy concern level, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a large statistically significant effect when comparing average IUIPC scores with the fraction of scenarios that each participant reported as being very upsetting ($\rho=0.446$, $p<0.0005$). Similarly, we observed that age was also a significant predictor of VUR ($\rho=0.121$, $p<0.0005$). We suspect that the age effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$), as others have also observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.

@@

At the same time, these perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits, but they do reflect the general public's present exposure to these technologies and also show that people do perceive specific risks and benefits. We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used. We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).

\subsection{Perceived Concerns for Wearable Devices}
So far, participants had responded to questions regarding specific scenarios or assessed technologies presented to them. For completeness of the survey, we also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants an open-ended question regarding the most likely risks associated with owning and interacting with wearable devices.

@@

This question was asked along with the demographics questions, near the end of the survey, but before any IUIPC questions regarding privacy, to avoid biasing. The participants were presented with a blank box to write in, with no character limit to their open-ended responses.

Without any doubt, the open-ended responses state that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}. This top concern surpassed all other concerns by about an order of magnitude or more:

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|r|r|}
\hline
Concern &  Responses &  Frequency   \\
\hline
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\% \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 185 & 10.42\%\\
Social Impact &	157 & 8.80\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\
\hline
\end{tabular}
\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
\label{open-responses}
\end{center}
\end{table}

Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such as battery burns or distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security). Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.

@@

\section{Discussion}
We take this section to discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.

\subsection{Future Research Directions}
Wearables are still in their infancy. Perceptions of situations and new capabilities will change rapidly with new capabilities and increased exposure, respectively. However, videos, and textual information is considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies. Various systems which can detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.

While privacy and security concerns were expected, consider these unexpected user concerns as starting points for future research: the high financial costs of wearables, health concerns of constant device use, safety issues related to device operation, the social impact of wearable devices, and improving aesthetics of wearables.

\subsection{Limitations}
One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo. We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables. However, that will also have its own bias and limitations as well, since they would not reflect the general population. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

@@

Recently Denning et. al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}. Participants in their study expressed concerns due to the subtle, easy-to-use, and potentially ubiquitous nature of wearables. While their research examined the privacy concerns of bystanders in the presence of wearable devices, we are aware of no work that has looked at the privacy concerns of the owners of the devices.

>>>>

\section{Introduction}
With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing. Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking. Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.

@@

To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}. A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns. The goal of this paper is to gain a better sense of what those concerns are.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies. However, we suspect that this may be due to a lack of exposure to these newer technologies.
%\item We report people's self-reported top concerns for wearable devices. Privacy, by far, is the top concern. Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms. 
\end{itemize}

@@

\subsection{Methodology Motivation}
\subsubsection{Smartphone Risk Scenarios}
Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risk scenarios. Participants were asked how upset they would be if a certain action had occurred without permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.

\subsubsection{Technology Risk Perception}
Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}. In their study, participants were asked to separately rate the risks and benefits for those technologies. They were told to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.

@@

We randomized the order participants completed sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.

@@

We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]

@@

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we also examined broad perceptions of new technologies and how those perceptions compared to other understood technologies. To this end, we modeled this section after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to rank several technologies by their relative risk and benefit to society. We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity. We chose these technologies because they represented varying levels of risks and benefits.

@@

\subsubsection{Additional Questions}
The exit portion of the survey firstly consisted of questions asking for age, gender, and education. Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices. We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.

@@

\subsection{Recruitment and Analysis Method}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above. Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants. We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784. Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).

@@

\subsection{Concern Factors}
In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone. We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.

\subsubsection{Data Type}
Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario. We present various statistical models in section \ref{sec:regression} to support this conclusion. Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types. The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.

@@

Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken). It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).

@@

\subsubsection{Data Recipient}
Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher. A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation. Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.

@@

We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans. We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]

@@

\subsubsection{Device Type}
Participants had unique VUR rates for scenarios only differing in device. Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}. However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.  The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.

@@

Participants' responses to scenarios were correlated with several demographic factors. First, we observed the biggest predictor, by far, of participants' decisions to rate a scenario as very upsetting was their self-reported general privacy concern level, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a large statistically significant effect when comparing average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$). Similarly, we observed that age was also a significant predictor of VUR ($\rho=0.121$, $p<0.0005$). We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.

@@

These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits. However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits. We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used. We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).

\subsection{Perceived Concerns for Wearable Devices}
We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:

@@

This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing). The participants were presented with a blank box to write in, with no character limit to their open-ended responses.

Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}. This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}). Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|r|}
\hline
Concern &  Responses &  Frequency   \\
\hline
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\% \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 185 & 10.42\%\\
Social Impact &	157 & 8.80\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\
\hline
\end{tabular}
\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
\label{openresponses}
\end{center}
\end{table}

@@

\section{Discussion}
Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.

\subsection{Future Research Directions}
Wearables are still in infancy. Perceptions of situations and capabilities will change rapidly with advancements and increased exposure. However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies. Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.

While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.

\subsection{Limitations}
One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo. We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables. However, that will also have its own biases and limitations, since this does not reflect the general population. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

@@

Recently Denning et. al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}. Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous). While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
